Optimizing and Incrementalizing Collection Queries by AST Transformations

### 2017-07-29 pldi14/sec-practice.tex
Revise pointer to removed chapter
Revise figure titles
Add shorter titles for ToC where needed, shorten existing titles where
appropriate.
Use "chapter conclusion" uniformly

In our current implementation, the code of the generated
derivatives can become quite big. For the histogram example
(which is around 1KB of code), a pretty-print of its derivative
is around 40KB of code. The function application case in
\cref{fig:correctness:derive} can lead to a quadratic growth in
the worst case. More importantly, we realized that our home-grown
transformation system in some cases performs overly aggressive
inlining, especially for derivatives, even though this is not
required for incrementalization, and believe this explains a
significant part of the problem. Indeed, code blowup problems do
not currently appear in later experiments (see
\cref{ch:inc-more-programs}). \pg{Revise forward pointer.}

\paragraph{Summary}
Our results show that the incrementalized program runs
in essentially constant time and hence orders of magnitude faster than
the alternative of recomputation from scratch.

@@

\begin{figure}
\includegraphics[keepaspectratio,width=8.5cm]{pldi14/HistogramGenerated-new.pdf}
\caption{Performance results in log-log scale, with input size on
  the x-axis and runtime in ms on the y-axis. Confidence
  intervals are shown by the whiskers; most whiskers are
  too small to be visible.}
\label{fig:graph}
\end{figure}

>>>>

In our current implementation, the code of the generated
derivatives can become quite big. For the histogram example
(which is around 1KB of code), a pretty-print of its derivative
is around 40KB of code. The function application case in
\cref{fig:correctness:derive} can lead to a quadratic growth in
the worst case. More importantly, we realized that our home-grown
transformation system in some cases performs overly aggressive
inlining, especially for derivatives, even though this is not
required for incrementalization, and believe this explains a
significant part of the problem. Indeed, code blowup problems do
not currently appear in later experiments (see
\cref{sec:case-studies}).

\section{Chapter conclusion}
Our results show that the incrementalized program runs
in essentially constant time and hence orders of magnitude faster than
the alternative of recomputation from scratch.

@@

\begin{figure}
\includegraphics[keepaspectratio,width=8.5cm]{pldi14/HistogramGenerated-new.pdf}
\caption[Performance results in $\log$--$\log$ scale]
{Performance results in $\log$--$\log$ scale, with input size on
  the x-axis and runtime in ms on the y-axis. Confidence
  intervals are shown by the whiskers; most whiskers are
  too small to be visible.}
\label{fig:graph}
\end{figure}
